### 2022-02-22 CV/cv-sections/papers.tex
CV update

>>>>

\cventry
{Dmitry Kovalev, Aleksandr Beznosikov, Abdurakhmon Sadiev, Michael Persiianov, Peter Richtárik, Alexander Gasnikov} % Authors
{Optimal Algorithms for Decentralized Stochastic Variational Inequalities} % Title
{\href{https://arxiv.org/abs/2202.02771}{arXiv 2022}} 
{06 Feb 2022} % Date
{}

\cventry
{Dmitry Kovalev, Alexander Gasnikov, Peter Richtárik} % Authors
{Accelerated Primal-Dual Gradient Method for Smooth and Convex-Concave Saddle-Point Problems with Bilinear Coupling} % Title
{\href{https://arxiv.org/abs/2112.15199}{arXiv 2021}} 
{30 Dec 2021} % Date
{}

\cventry
{Aleksandr Beznosikov, Alexander Rogozin, Dmitry Kovalev, Alexander Gasnikov} % Authors
{Near-Optimal Decentralized Algorithms for Saddle Point Problems over Time-Varying Networks} % Title
{\href{https://arxiv.org/abs/2107.05957}{arXiv 2021}} 
{13 Jul 2021} % Date
{}

\cventry
{Dmitry Kovalev, Elnur Gasanov, Peter Richtárik, Alexander Gasnikov} % Authors
{Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks} % Title
{\href{https://proceedings.neurips.cc/paper/2021/hash/bc37e109d92bdc1ea71da6c919d54907-Abstract.html}{NeurIPS 2021}} 
{08 Jun 2021} % Date
{}
